### 2009-09-24 doc/tech_doc/a-rex/arex_tech_doc.tex
add SLURM backend (copied from arc0/trunk)
port gm-jobs utility from arc0. I will let the release coordinators decide whether to put on the final release branch

\begin{itemize}
\item \textit{smtp-send.sh} and \textit{smtp-send} -- These are the modules
responsible for sending e-mail notifications to the user. The format
of the mail messages can be easily changed by editing the simple shell
script \textit{smtp-send.sh}. 
\item \textit{submit-{*}-job} -- Here {*} stands for the name of the LRMS.
Currently supported LRMS are PBS/Torque, Condor, LoadLeveler, LSF
and SGE. Also \emph{fork} pseudo-LRMS is supported for testing purposes.
This module is responsible for job submission to the LRMS.
\item \textit{cancel-{*}-job} -- This script is for canceling jobs which
have been already submitted to the LRMS.
\item \textit{scan-{*}-job} -This shell script is responsible for notifying
the A-REX about completion of jobs. It's implementation for PBS uses
server logs to extract information about jobs. If logs are not available
it uses the less reliable \emph{qstat} command for that. Other backends
use different techniques.
\end{itemize}

\begin{comment}In addition, there is also an administration utility:

\begin{itemize}
\item \textit{gm-jobs} -- prints a list of jobs available on the cluster
and the number of jobs in each state.\\
\hspace*{0.5cm}gm-jobs {[}-h] {[}-l] {[}-u uid] {[}-U name]\\
\hspace*{0.5cm}-l -- print more information about each job,\\
\hspace*{0.5cm}-u -- pretend utility is run by user with id \emph{uid},\\
\hspace*{0.5cm}-U -- pretend utility is run by user with name \emph{name}.
\end{itemize}
\end{comment}

>>>>

\begin{itemize}
\item \textit{smtp-send.sh} and \textit{smtp-send} -- These are the modules
responsible for sending e-mail notifications to the user. The format
of the mail messages can be easily changed by editing the simple shell
script \textit{smtp-send.sh}. 
\item \textit{submit-{*}-job} -- Here {*} stands for the name of the LRMS.
Currently supported LRMS are PBS/Torque, Condor, LoadLeveler, LSF, SLURM,
and SGE. Also \emph{fork} pseudo-LRMS is supported for testing purposes.
This module is responsible for job submission to the LRMS.
\item \textit{cancel-{*}-job} -- This script is for canceling jobs which
have been already submitted to the LRMS.
\item \textit{scan-{*}-job} -This shell script is responsible for notifying
the A-REX about completion of jobs. It's implementation for PBS uses
server logs to extract information about jobs. If logs are not available
it uses the less reliable \emph{qstat} command for that. Other backends
use different techniques.
\end{itemize}

In addition, there is also an administration utility:

\begin{itemize}
\item \textit{gm-jobs} -- prints a list of jobs available on the cluster
and the number of jobs in each state.\\
\hspace*{0.5cm}gm-jobs {[}-h] {[}-l] {[}-u uid] {[}-U name] {[}-c conf\_file] {[}-d control\_dir]\\
\hspace*{0.5cm}-h -- print short help,\\
\hspace*{0.5cm}-l -- print more information about each job,\\
\hspace*{0.5cm}-u -- pretend utility is run by user with id \emph{uid},\\
\hspace*{0.5cm}-U -- pretend utility is run by user with name \emph{name},\\
\hspace*{0.5cm}-c -- use specified configuration file,\\
\hspace*{0.5cm}-d -- read information from specified control dir.
\end{itemize}
